---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Introduction

The goal of `vemirt` is to detect differential item functioning (DIF) in two-parameter logistic (2PL) models via (Gaussian variational) expectation-maximization estimation.

## Installation

You can install the development version of `vemirt` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("weiconglyu/vemirt")
```

## Example

This is a basic example which shows you how to apply Gaussian variational expectation-maximization estimation with importance sampling to the simulated data from the package:

```{r example}
library(vemirt)
result <- with(DIF_simdata, DIF_GVEMM(Y, D, X, 'IWGVEMM', Lambda0 = c(0.3, 0.5)))
round(result[[1]]$beta, 3)
round(result[[2]]$beta, 3)
```
